\bf Model Visualization Techniques for a Social Network Model

### 2017-03-29 paper.Rnw
forgot to push previous changes

\par The software SIENA, and its \texttt{R} implementation \texttt{RSiena}, was developed by \citet{RSiena} to estimate the parameters of the SAOMs, among other social network models. This software is a huge contribution to the field of social network analysis, and when we began working with it we were eager to understand how it works. To better understand the \texttt{RSiena} software and the SAOMs themselves, we use the principals of model visualization from \citet{modelvis}. With the work of \citet{modelvis} guiding us, we explore RSiena and SAOMs with innovative visualizations, both static and dynamic. By bringing some light to the underlying methods and structures "behind the scenes" of SAOMs and RSiena, we will help other researchers working with the models better understand and better use these models.

@@

There are two primary methods used to visualize networks. The first method represents nodes with points in 2D Euclidean space and then represents edges by connecting the points with lines when there is an edge between the two nodes. But, because there is no natural placement of the points, a random placement is used, then adjusted iteratively via a layout algorithm, of which there are many.

@@

<<getdata, results='asis'>>=

nulls <- read.csv("data/distribution_null_model.csv")
alt <- read.csv("data/distribution_jumpTT_model.csv")
alt2nd <- read.csv("data/distribution_dblpairs_model.csv")
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
means <- simu2 %>% group_by(Model, parameter) %>% summarize(
  means = mean(estimate)
)
library(dplyr)
null_mod_sv <- as.numeric(nulls[,-c(1,6,7)] %>% summarise_each(funs(mean)))
alt_mod_sv <- as.numeric(alt[,-c(1, 7,8)] %>% summarise_each(funs(mean)))
alt_mod2_sv <- as.numeric(alt2nd[,-c(1,7,8)] %>% summarise_each(funs(mean)))
@

>>>>

\par The software SIENA, and its \texttt{R} implementation \texttt{RSiena}, was developed by \citet{RSiena} to estimate the parameters of the SAOMs, among other social network models. This software is a huge contribution to the field of social network analysis, and when we began working with it we were eager to understand how it works. To better understand the \texttt{RSiena} software and the SAOMs themselves, we combine the principals of network visualization with those of model visualization from \citet{modelvis}. With the work of \citet{modelvis} guiding us, we explore RSiena and SAOMs with innovative network visualizations, both static and dynamic. By bringing some light to the underlying methods and structures "behind the scenes" of SAOMs and RSiena, we will help other researchers working with the models better understand and better use these models.

@@

There are two primary methods used to visualize networks. The first method, often referred to as node-link diagrams, represents nodes with points in 2D Euclidean space and then represents edges by connecting the points with lines when there is an edge between the two nodes. But, because there is no natural placement of the points, a random placement is used, then adjusted iteratively via a layout algorithm, of which there are many.

@@

<<getdata, results='asis'>>=
nulls <- read.csv("data/distribution_null_model.csv")
alt <- read.csv("data/distribution_jumpTT_model.csv")
alt2nd <- read.csv("data/distribution_dblpairs_model.csv")
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
means <- simu2 %>% group_by(Model, parameter) %>% summarize(
  means = mean(estimate)
)
library(dplyr)
null_mod_sv <- as.numeric(nulls[,-c(1,6,7)] %>% summarise_each(funs(mean)))
alt_mod_sv <- as.numeric(alt[,-c(1, 7,8)] %>% summarise_each(funs(mean)))
alt_mod2_sv <- as.numeric(alt2nd[,-c(1,7,8)] %>% summarise_each(funs(mean)))
@
